---
output: rmarkdown::github_document
---

`pastebin` : Tools to work with the pastebin API

**WIP!! The package API will very likely be in rapid change mode for a bit**

The following functions are implemented:

- `get_paste`:	Get raw paste data
- `get_paste_metadata`:	Get paste metadata
- `get_recent_pastes`:	Get recent pastes
- `new_paste`:	Create a new paste
- `pastebin_api_key`:	Get or set PASTEBIN_API_KEY value
- `toString.paste`:	Extract just the paste text from a paste object

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/pastebin")
```

```{r message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(pastebin)
library(tidyverse)

# current verison
packageVersion("pastebin")

r_pastes <- get_recent_pastes(lang="rsplus")

glimpse(r_pastes)
```

Can't always trust the `lang` setting. Some non-R stuff in there:

```{r message=FALSE}
walk(r_pastes$key[1:10], ~print(toString(get_paste(.))))
```

Since the user is obvious:

```{r message}
mebbe_r <- filter(r_pastes, user != "AllRls_net")
walk(mebbe_r$key, ~print(toString(get_paste(.))))
```

### Test Results

```{r message=FALSE, warning=FALSE, error=FALSE}
library(pastebin)
library(testthat)

date()

test_dir("tests/")
```

